Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-09 paper.qmd
deployments and tracking section

![Deployments map](deploy.gif)

<p>The next tab is the <em>Chosen bird</em> tab. </p>

>>>>

![Deployments map](deploy.gif){.lightbox}

<p>The next tab is the <em>Chosen bird</em> tab. In the <em>Table</em> nested tab: first, we have a page that shows the immediate data for the bird that was chosen from its deployment, then we have a map of the locations where this bird has pinged a receiver.In the <em>Group</em> nested tab we have a similar map, but it shows the pings for each of the birds deployed from the same deployment site. The lines are weighted by the frequency of the amount of birds that travelled there. </p>

![Chosen bird map](chosenbird.png){.lightbox}
![Chosen group map](chosengroup.png){.lightbox}
